PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-15 paper/ms.tex
update disk discussion

Based on the lack of an infrared excess seen by \citet{yu_tests_2015},
the primordial gas disks seem to be have been depleted\footnote{A
potential confounding factor is completeness. Is Spitzer sensitive to
infrared excesses at the distance of Orion? The series of studies by
\cite{hernandez_spitzer_2006,hernandez_spitzer_ob1_2007,hernandez_spitzer_sig_2007,hernandez_spitzer_2009}
show that it is.}
% JNW: I don't understand why we can be so definitive...
% an infrared excess is not either 'present' or 'absent'. The upper limit in Jy
% corresponds to a constraint on the mass/radius/etc of any dusty disk.
around both stars in \ptfo. The stars are therefore no longer
magnetically locked to their disks.  This is consistent with the
$\approx$half-day periodicities of both rotation signals: young disked
M dwarfs typically rotate with periods of two days or more due to
magnetic locking \citep[{\it e.g.},][]{rebull_rotation_2020}.  If the
two stars are within $\approx$50$\,$AU of each other, as required by
the NIRC2 adaptive optics imaging, then it would also be expected that
the stars would have truncated the outer edges of their respective
disks, in a manner seen at the population level in exoplanetary
systems \citep{kraus_impact_2016,moe_impact_2019}.

The key remaining question is what causes the transient dips. This is
an unsolved problem not only for \ptfo\ but also for the emerging
class of similar young and rapidly rotating M-dwarfs.  Many possible
explanations were discussed by \citet{rebull_rotation_2016},
\citet{david_transient_2017}, \citet{stauffer_orbiting_2017}, and
\citet{zhan_complex_2019}.  Among the {\it disfavored} explanations
are that the dips are caused by
{\it (i)} eclipsing binaries;
{\it (ii)} ``dipper''-flavor Class-I or Class-II disks;
{\it (iii)} eclipses of prominences;
% JNW: why is this one ruled out? Sounds similar to the accretion-hotspot hypothesis.
{\it (iv)} high-latitude accretion hotspots;
{\it (v)} high-latitude starspots;
or
{\it (vi)} dust clouds of plausible composition.
We also view the possibility of {\it (vii)} tidally disrupted
planetary or cometary material to be implausible, given the
synchronicity between dip and rotation periods seen across many
systems.
% JNW Could the material get magnetically locked at the corotation radius?

>>>>

Based on the lack of an infrared excess seen by \citet{yu_tests_2015},
the primordial gas disks of both stars in \ptfo\ seem to be have been
depleted.  This is consistent with the $8.5\pm1.2\,{\rm Myr}$ age of
the 25$\,$Ori-1 group, and the rapid rate at which stars show lose
their disks between 1 and 10$\,$Myr \citep[{\it
e.g.},][]{hernandez_spitzer_ob1_2007}.  The stars are therefore
presumably no longer magnetically locked to their disks.  This is also
suggested by the $\approx$half-day periodicities of both rotation
signals: young disked M dwarfs typically rotate with periods of two
days or more due to magnetic locking \citep[{\it
e.g.},][]{rebull_rotation_2020}.  If the two stars are within
$\approx$50$\,$AU of each other, as required by the NIRC2 adaptive
optics imaging, then it would also be expected that the stars would
have truncated the outer edges of their respective disks, in a manner
seen at the population level in exoplanetary systems
\citep{kraus_impact_2016,moe_impact_2019}.

The key question is what causes the transient dips. This is
an unsolved problem not only for \ptfo\ but also for the emerging
class of similar young and rapidly rotating M-dwarfs.  Many possible
explanations were discussed by \citet{rebull_rotation_2016},
\citet{david_transient_2017}, \citet{stauffer_orbiting_2017}, and
\citet{zhan_complex_2019}.  Among the {\it disfavored} explanations
are that the dips are caused by
{\it (i)} eclipsing binaries;
{\it (ii)} ``dipper''-flavor Class-I or Class-II disks;
{\it (iii)} eclipses of prominences;
% JNW: why is this one ruled out? Sounds similar to the accretion-hotspot hypothesis.
{\it (iv)} high-latitude accretion hotspots;
{\it (v)} high-latitude starspots;
or
{\it (vi)} dust clouds of plausible composition.
We also view the possibility of {\it (vii)} tidally disrupted
planetary or cometary material to be implausible, given the
synchronicity between dip and rotation periods seen across many
systems.
% JNW Could the material get magnetically locked at the corotation radius?
